---
title: "REPORT NAME"
author:

subtitle: "Assignment report"
date: "University of Sydney | Data2002 | 7/11/2020"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

# Abstract

#### Initial Data Analysis
```{r}

library(ggplot2)
library(readr)
library(tidyverse)
library(janitor)
library(knitr)
library(dplyr)
library(skimr)
library(visdat)
```

```{r}
data = readr::read_csv("housing_prices.csv")
```
##### Introduction
The housing_prices.csv document provides a detail data collection of a random sample of 1734 houses taken from full Saratoga Housing Data. The dataset has 17 variables which represents a range of housing prices based on related housing properties. This project aims at studying the association between the house prices and their related properties by multiple regression model and try to predict the housing prices based on their properties by using the model. Below is a brief description of each variable. 

Price: Housing prizes in US dollars.

Lot.Size: Size of lot in acres.

Waterfront: Whether the house includes waterfront. 1 refers to TRUE, 0 refers to FALSE.

Age: The age of the house in years.

Land.Value: The value of the land where the house is located.

New.Construct: Whether the house is a new construction. 1 refers to TRUE, 0 refers to FALSE.

Central.Air: Whether the house has central air conditioner. 1 refers to TRUE, 0 refers to FALSE.

Fuel.Type: 5 different types of fuel used for heating including electric, gas, oil, wood, solar.

Heat.Type: 3 types of heating system including electric, hot water, hot air

Sewer.Type: 2 types of sewer system, private and public.

Living.Area: Living area in square feet.

Pct.College: Percentage of neighbourhoods that graduated from college.

Bedrooms: Numbers of bedrooms.

Fireplaces: Numbers of fireplaces.

Bathrooms: Numbers of bathrooms.

Rooms: Total numbers of rooms.

Test: ???

### Bias
In a random sample, this data set only collect the details of house price in Saratoga which is a small town that can not represent house price in New York, because different area like central and countryside that have different living environment and around facilities which will influence the house price. Secondly, as zero conditional mean that there have missing variables, for instance, the location of the house is convenient for transportation, whether there are subway stations and bus stops nearby; whether there are security hazards in the area where the house is located, low crime rate and comprehensive security measures. Furthermore, the measure bias, there has no specific unit of loft-size, land value, living area that there may exist the error of measuring, then for perfect col-linearity, the number of total room equal to bedrooms plus bathrooms plus other rooms that may repeat then lead to bias.

##### Data Cleaning
```{r} 
data = data %>% janitor::clean_names()
# data
```

```{r}
# 1.Price (drop rows with NA)
price = data$price
price[price == ""] = NA
price = na.omit(price)
```

```{r}
# 2.Lot.Size (drop rows with NA)
lot_size = data$lot_size
lot_size[lot_size == ""] = NA
lot_size = na.omit(lot_size)

```

```{r}
# 3.Waterfront (drop rows with NA)
waterfront = data$waterfront
waterfront[waterfront == ""] = NA
waterfront = na.omit(waterfront)
```

```{r}
# 4.Age (drop rows with NA)
age = data$age
age[age == ""] = NA
age = na.omit(age)
```

```{r}
# 5.Land.Value (drop rows with NA)
land_value = data$land_value
land_value[land_value == ""] = NA
land_value = na.omit(land_value)
```

```{r}
# 6.New.Construct (drop rows with NA)
new_construct = data$new_construct
new_construct[new_construct == ""] = NA
new_construct = na.omit(new_construct)
```

```{r}
# 7.Central.Air (drop rows with NA)
central_air = data$central_air
central_air[central_air == ""] = NA
central_air = na.omit(central_air)
```

```{r}
# 8.Fuel.Type (Change categorical data to numerical)

# (unique(data$Fuel.Type))
fuel_type = data$fuel_type
fuel_type[fuel_type == "Electric"] = 1
fuel_type[fuel_type == "Gas"] = 2
fuel_type[fuel_type == "Oil"] = 3
fuel_type[fuel_type == "Wood"] = 4
fuel_type[fuel_type == "None"] = NA
fuel_type[fuel_type == "Solar"] = 5
fuel_type[fuel_type == "Unknown/Other"] = NA
fuel_type = na.omit(fuel_type)
fuel_type <- as.numeric(fuel_type)
# (unique(fuel_type))
```

```{r}
# 9.Heat.Type (Change categorical data to numerical)

# (unique(data$heat_type))
heat_type = data$heat_type
heat_type[heat_type == "Electric"] = 1
heat_type[heat_type == "Hot Water"] = 2
heat_type[heat_type == "None"] = NA
heat_type = suppressWarnings(as.numeric(c("1", "2", "X")))
heat_type = na.omit(heat_type)
heat_type
# (unique(heat_type))
```

```{r}
# 10.Sewer.Type (Change categorical data to numerical)

# (unique(data$sewer_type))
sewer_type = data$sewer_type
sewer_type[sewer_type == "Private"] = 1
sewer_type[sewer_type == "Public"] = 2
sewer_type[sewer_type == "None/Unknown"] = NA
sewer_type = na.omit(sewer_type)
sewer_type <- as.numeric(sewer_type)
# (unique(sewer_type))
```

```{r}
# 11.Living Area (drop rows with NA)
living_area = data$living_area
living_area[living_area == ""] = NA
living_area = na.omit(living_area)
```

```{r}
# 12.Pct_college (drop rows with NA)
pct_college = data$pct_college
pct_college[pct_college == ""] = NA
pct_college = na.omit(pct_college)
```

```{r}
# 13.Bedrooms (drop rows with NA)
bedrooms = data$bedrooms
bedrooms[bedrooms == ""] = NA
bedrooms = na.omit(bedrooms)
```

```{r}
# 14.Fireplaces (drop rows with NA)
fireplaces = data$fireplaces
fireplaces[fireplaces == ""] = NA
fireplaces = na.omit(fireplaces)
```

```{r}
# 15.Bathrooms (drop rows with NA)
bathrooms = data$bathrooms
bathrooms[bathrooms == ""] = NA
bathrooms = na.omit(bathrooms)
```

```{r}
# 16.Rooms (drop rows with NA)
rooms = data$rooms
rooms[rooms == ""] = NA
rooms = na.omit(rooms)
```

```{r}
# 17.Test (drop rows with NA)
test = data$test
test[fireplaces == ""] = NA
test = na.omit(test)
```

##### Limitations: 

##### Bias: 
The housing prices may also be affected by different suburbs they are located in but it is not indicated.




# IDA
```{r load_libraries,message = FALSE,results = "hide", warning=FALSE}

```

# Assumption

# Analysis
#Back/Forward selection 
aaaaaa

## Multi-Regression Model
```{r}
lm1 = lm(log(price)~ lot_size+ waterfront+ age+ land_value+new_construct+central_air+fuel_type+heat_type+sewer_type+living_area+pct_college+bedrooms+fireplaces+bathrooms+rooms+test, data =data)

summary(lm1)

#step.back.aic = step(lm3, 
          #           direction = "backward", 
           #          trace = FALSE)
#round(summary(step.back.aic)$coef,3)


```
```{r}

step.back.aic = step(lm1, 
                     direction = "backward", 
                     trace = FALSE)
round(summary(step.back.aic)$coef,3)

step.back.aic %>%
  broom::glance() %>% 
  round(2) %>% t()


drop1(step.back.aic, test = "F")


```


```{r}
#Graph involve in the analysis 
fit = lm1
 plot(fit)

```



```{r}
lm2 = lm(price ~ lot_size, data = data)

new_temp = data.frame(lot_size = seq(from = min(lot_size),
                                        to = max(lot_size),
                                        by = 0.1))

pi = predict(lm2, new_temp, interval = "prediction", level = 0.90)
ci = predict(lm2, new_temp, interval = "confidence", level = 0.90)
interval_df = data.frame(
  pi_upper = pi[,"upr"],
  pi_lower = pi[,"lwr"],
  ci_upper = ci[,"upr"],
  ci_lower = ci[,"lwr"],
  temperature = new_temp$temperature
)

```

# Limitations
# Results  
# Conclusion
# References

